### 2016-06-03 w-wires/paper_gerasimovda.tex
Estimation for first part

\subsubsection*{Case 2: $y > Z$}
For $y > Z$, 
\[
s_1(x + \iu y) 
 = \frac{\tanh y - \frac{2 W}{W^2 + 1}}{\tanh y + \frac{2 W}{W^2 + 1}}
 = 1 - 2 \frac{\frac{2 W}{W^2 + 1}}{\tanh y + \frac{2 W}{W^2 + 1}}
\]

@@

\subsection*{Proofs of convergence for logarithmic parts}

\todo{Unit cicle in Cayley space maps to $R$, and $\ln\abs{\det S}$ on $R$ is zero everywhere}

\subsection*{Proof of convergence}

\[
l(x + \iu y) =
\begin{cases}
 \\
s_2'(Z)(y - Z)                       &, Z_0 < y \le Z \\
\frac{s_1(C + R)}{C + R - Z} (y - Z) &, y > Z
\end{cases}
\]

\todo{full circle; explain what is $\phi$}
\begin{align*}
    & \int\limits_{t = \phi}^{\frac{\pi}{2}} \ln^2 s(R \eexp{\iu t} + \iu C) \frac{R}{\norm{R \eexp{\iu t} + \iu C + i}^2} dt\\
=   & \int\limits_{t = \phi}^{\frac{\pi}{2}} \ln^2 f(R \sin t + C) \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} dt\\
\le & \int\limits_{t = \phi}^{\frac{\pi}{2}} \ln^2 f(R \sin t + C) \frac{R}{R^2 \cos^2 t + (R \sin t + C)^2} dt\\
\end{align*}

@@

\begin{align*}
    & \int\limits_{y = Z}^{R + C} \ln^2 f(y) \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} dy \\
=   & \int\limits_{y = Z}^{R + C} \ln^2 f(y) \frac{R}{R^2 - (C - y)^2 + (y + 1)^2} \frac{1}{\sqrt{R^2 - (C - y)^2}} dy\\
=   & \int\limits_{y = Z}^{R + C} \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 C y + 1} \frac{1}{\sqrt{(R - C + y)}} \frac{1}{\sqrt{(R + C - y)}} dy\\
\end{align*}

>>>>

\subsubsection*{Case 2: $y > Z$}
For $y > Z$, 
\[
s_1(x + \iu y) 
 = \frac{\tanh y - V}{\tanh y + V}
 = 1 - 2 \frac{V}{\tanh y + V}
\]

@@

\todo{Ask Popov? Add to slides?? Unit cicle in Cayley space maps to $R$, and $\ln\abs{\det S}$ on $R$ is zero everywhere}

% \subsection*{Proof of convergence}

% \[
% l(x + \iu y) =
% \begin{cases}
%  \\
% s_2'(Z)(y - Z)                       &, Z_0 < y \le Z \\
% \frac{s_1(C + R)}{C + R - Z} (y - Z) &, y > Z
% \end{cases}
% \]

\todo{full circle; explain what is $\phi$}

\todo{move up, this is relevant to every piece}
\begin{align*}
    & \int\limits_{t = \phi}^{\frac{\pi}{2}} \ln^2 s(R \eexp{\iu t} + \iu C) \frac{R}{\norm{R \eexp{\iu t} + \iu C + i}^2} dt\\
=   & \int\limits_{t = \phi}^{\frac{\pi}{2}} \ln^2 f(R \sin t + C) \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} dt\\
\le & \int\limits_{t = \phi}^{\frac{\pi}{2}} \ln^2 f(R \sin t + C) \frac{R}{R^2 \cos^2 t + (R \sin t + C)^2} dt\\
\end{align*}

@@

\begin{align*}
    & \int\limits_{y = Z}^{R + C} \ln^2 f(y) \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} dy \\
=   & \int\limits_{y = Z}^{R + C} \ln^2 f(y) \frac{R}{R^2 - (C - y)^2 + (y + 1)^2} \frac{1}{\sqrt{R^2 - (C - y)^2}} dy\\
=   & \int\limits_{y = Z}^{R + C} \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}}  dy\\
\end{align*}

First, notice that for $Z \le y \le R + C$:
\begin{align*}
    & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}} \\
\le & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\end{align*}

To estimate, we will split the integration in three parts:

\subsection*{from $Z$ to $Z + \frac{1}{R}$}

\begin{align*}
       & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\\ \le & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) Z + 1} \frac{1}{\sqrt{R + C - (Z + \frac{1}{R})}} \frac{1}{\sqrt{R - C + Z}}
% \\  = & \ln^2 f(y) \mcO()
\end{align*}

% TODO REFERENCE!
$\int\limits_{Z}^{Z + \frac{1}{R}} \ln^2 f(y) dy$ is easy to compute directly, using the fact that:

\[
    \int\limits_b^{b + c} \ln^2 (a (x - b)) dx = c (\ln^2(a c) - 2 \ln (a c) + 2)
\]

Hence, $\int\limits_{Z}^{Z + \frac{1}{R}} \ln^2 f(y) dy = \frac{1}{R} ( \ln^2 (\frac{s_1(C + R)}{C + R - Z} \frac{1}{R}) - 2 \ln (\frac{s_1(C + R)}{C + R - Z} \frac{1}{R}) + 2)$, which clearly is $\mcO(\frac{\ln^2(C + R - Z)}{R})$. Taking into account that the constant coefficient before the integral is of order $\frac{1}{\sqrt{R}}$ \todo{???}, it is clear that the first part goes to $0$ as $R, C \to \infty$.
